Visualization and analysis of probability distributions of large temporal data

### 2021-11-10 Rmd/00-c-declaration.Rmd
Rob's corrections

Three publications are included in this thesis, one of which has been accepted for publication in the Journal of Computational and Graphical Statistics (@Gupta2021-gravitas). Two others have not yet been submitted. "Exploring probability distributions across cyclic temporal granularities" is the central theme of the thesis. All of the papers in the thesis were conceptualized, developed, and written by myself, the student, while working in the Department of Econometrics and Business Statistics under the supervision of Professor Rob J Hyndman and Professor Dianne Cook. When co-authors are listed, it indicates that the work was produced through active collaboration between researchers and that their contributions to team-based research have been recognized. The following table details the work, including
my and my fellow co-authors contributions:

@@

I have not renumbered sections of submitted or published papers in order to generate a consistent presentation within the thesis.

>>>>

Three publications are included in this thesis, one of which has been accepted for publication in the _Journal of Computational and Graphical Statistics_ (@Gupta2021-gravitas). Two others have not yet been submitted. "Exploring probability distributions across cyclic temporal granularities" is the central theme of the thesis. All of the papers in the thesis were conceptualized, developed, and written by myself, the student, while working in the Department of Econometrics and Business Statistics under the supervision of Professor Rob J Hyndman and Professor Dianne Cook. When co-authors are listed, it indicates that the work was produced through active collaboration between researchers and that their contributions to team-based research have been recognized. The following table details the work, including
my and my fellow co-authors contributions:

@@

I have renumbered sections of submitted or published papers in order to generate a consistent presentation within the thesis.
